---
title: "Match-Swansea"
author: "Peje"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Login 
```{r login, echo = FALSE, include = FALSE}
source('../../filepaths.R') # read in filepaths
source(paste0(main_project_path, '1429_RODBC_login_20221031.R'))
source(paste0(cohort_creation_path, 'functions/1429_matching_functions_peje_20221107.R'))
source(paste0(cohort_creation_path, 'functions/1429_Exclusion_criteria_filter_PostMatching_peje_20221103.R'))
```



# Load libraries
```{r, load_lib, echo = FALSE, include = FALSE}
library(dplyr)
library(lubridate)
library(openxlsx)
library(ggplot2)
library(stats)
library(tigerstats)
library(sqldf)
library(AMR)
library(cobalt)
library(hrbrthemes)
```

#remove unneeded vars
```{r, echo = FALSE, include = FALSE}
rm(list=ls()[! ls() %in% c("login","npt_matchingpool_raw","swa_uc_raw","swa_matchingpool_GPRegLkup","swa_matchingpool_LSOALkup","RUC_lkup","WIMD19Quin_lkup", "swa_mp_unpaidcarerevent")])
```



# Import data from eclipse
# - initialise WIMD levels and accompanying description
# - import tables 
```{r import_data, echo = FALSE, include = FALSE}

# initialise WIMD levels and accompanying description
WIMD19Quin_lkup <- data.frame(
  WIMD = c(1,2,3,4,5),
  WIMD_DESC = c("1. Most deprived","2","3","4","5. Least deprived"))

RUC_lkup <- sqlQuery(sql, "SELECT DISTINCT RUC11CD, RUC11 AS RUC11_DESC  FROM SAILREFRV.RURAL_URBAN_CLASS_2011_OF_LLSOAREAS_IN_ENG_AND_WAL")

swa_matchingpool_raw <- sqlQuery(sql, "SELECT * FROM SAILW1429V.PEJE_GPMATCHINGPOOL_SWANSEA")
swa_uc_raw <- sqlQuery(sql, "SELECT * FROM SAILW1429V.PEJE_DEDUP_GP_LA_SWANSEA")
mp_unpaidcarerevent <- sqlQuery(sql,"SELECT DISTINCT ALF_PE, EVENT_DT FROM SAILW1429V.PEJE_GPMATCHINGPOOL_UNPAIDCARERSCODES_SWANSEA")
matchingpool_GPRegLkup <- sqlQuery(sql, "SELECT * FROM SAILW1429V.PEJE_GPMATCHINGPOOL_GPREGLKUP_SWANSEA")
matchingpool_LSOALkup <- sqlQuery(sql, "SELECT * FROM SAILW1429V.PEJE_GPMATCHINGPOOL_LSOALKUP_SWANSEA")

```


# Data preparation
# - subset baseline characteristics required for matching in unpaid carers data
# -- join WIMD description
# -- run dataprep function on df
# - subset baseline characteristics required for matching in matching pool data
# -- run dataprep function on df
```{r echo = FALSE, include = FALSE}
#subset baseline characteristics for Unpaid carers
UnpaidCarers_df <- swa_uc_raw[, c("ALF_PE", "WOB","DEATH_DT","SEX", "AGE_STUDYSTART", "LSOA2011_CD","WIMD","RUC11CD","RUC11_DESC", "IDENTIFIEDBY")]

# join desc for WIMD
UnpaidCarers_df <- UnpaidCarers_df %>%  merge(WIMD19Quin_lkup, by.x= "WIMD", by.y="WIMD")
UnpaidCarers_baseline <- dataprep(UnpaidCarers_df)

#subset baseline characteristics for general population
MatchingPool_df <- swa_matchingpool_raw[, c("ALF_PE","WOB", "DEATH_DT","SEX", "AGE_STUDYSTART")]
MatchingPool_baseline <- dataprep(MatchingPool_df)

```


# Perform match using exact match
```{r echo = FALSE, include = FALSE}
swa_matchedOutput1 <- run_exactmatch(UnpaidCarers_baseline, MatchingPool_baseline)
swa_matchedOutput2 <- match.data(swa_matchedOutput1)
```


# Create sequence flags
# In Exact match, cases and controls with similar characteristics are placed in the same subclass. Hence, there can be >1 case and control in each subclass.
# - create a sequence number of cases (unpaid carers) in each subclass and select the maximum sequence number (i.e total unpaid carers per subclass)
# - merge this the max sequence number for each subclass back to the case and controls only table
# - merge extended information
# - clean the controls dataframe
# -- add TreatSeq col
# -- select required cols
# -- merge extended information (RUC, wimd description, etc)
```{r echo = FALSE, include = FALSE}
# create sequence for cases within each subclass
casesOnly1 <- swa_matchedOutput2 %>% filter(treat == 1) %>% 
  group_by(subclass) %>% 
  arrange(subclass, ALF_PE) %>%
  mutate(treatSeq = row_number()) %>%
  ungroup()


# max for each subclass where treat = 1 (i.e. total number of unpaid carers in each subclass)
maxSeq <- casesOnly1 %>% group_by(subclass) %>% 
  filter(treatSeq == max(treatSeq)) %>% ungroup() %>% select(subclass, treatSeq)

names(maxSeq)[2] <- "MaxTreatSeq"

casesOnly2 <- casesOnly1 %>% merge(maxSeq, by = "subclass", all.x =TRUE)

swa_matched_1 <- casesOnly2 %>% 
  merge(UnpaidCarers_baseline[, c("ALF_PE","SEX", "AGE_STUDYSTART", "LSOA2011_CD","WIMD","WIMD_DESC", "RUC11_DESC" )] , by="ALF_PE", all.x=TRUE)

# select controls only and merge with max treatSeq
controlsOnly1 <- swa_matchedOutput2 %>% filter(treat == 0)  %>% merge(maxSeq, by = "subclass", all.x =TRUE)

# add treatSeq column to match number of columns in casesOnly
controlsOnly2 <- controlsOnly1 %>% mutate(treatSeq = NA)

# select needed columns from controlsOnly df
controlsOnly3 <- controlsOnly2[, names(casesOnly2)]

# join merged data with extended information (RUC, wimd description,)
swa_matched_0 <- controlsOnly3 %>% 
  merge(MatchingPool_baseline[, c("ALF_PE","SEX", "AGE_STUDYSTART" )] , by="ALF_PE", all.x=TRUE)

```



# impute index dates
# - Prepare unpaid carers dataset
# -- create a subset of the data with required columns for unpaid carers
# -- add above to unpaid carers dataset
# -- add index date 
# -- calcuate are at index date
# - run function to get 1-1 match between unpaid carers and non-carers
# - perform checks (no duplicates, ratio and counts)
# - add ethnicity data to the 1-1 matched df
# - select columns in specified order
```{r echo = FALSE, include = FALSE}
#create  subsets of data
s_assmtdt <- sqldf("SELECT m.ALF_PE, m.subclass, m.treatSeq, u.IDENTIFIEDBY, FIRST_IDENTIFIED_DATE, FIRST_ASSESS, LAST_ASSESS, NUMBEROFCARERASSESSMENTCOMPLETED
      FROM swa_matched_1 m LEFT JOIN 
      (SELECT ALF_PE, IDENTIFIEDBY, FIRST_IDENTIFIED_DATE, FIRST_ASSESS, LAST_ASSESS, NUMBEROFCARERASSESSMENTCOMPLETED FROM swa_uc_raw) u
      ON m.ALF_PE = u.ALF_PE
      WHERE m.treat=1")


# rename for consistency
names(s_assmtdt)[6:ncol(s_assmtdt)] <- c("FIRST_CARER_ASSMT", "LATEST_CARER_ASSMT", "TOTAL_NUM_ASSESSMENTS")

# add index dates back to carers
swa_matched_1_full <- swa_matched_1 %>% merge(subset(s_assmtdt, select=-c(subclass, treatSeq)), by= "ALF_PE", all.x=TRUE)

# add age at index date for unpaid carers
swa_matched_1_full <- swa_matched_1_full %>% mutate(AGE_INDEXDATE = floor(time_length( difftime(FIRST_IDENTIFIED_DATE , WOB ), "years" ))) 

# run function to select controls
newly_matched_df <- extract_right_controls(swa_matched_1_full, swa_matched_0 )


#check ratio
ratio_df <- newly_matched_df %>%
  select(ALF_PE, treat, IDENTIFIEDBY) %>%  
  distinct_all() %>% 
  group_by(treat, IDENTIFIEDBY) %>% 
  summarise(total = n())



# Add ethnicity data
matched_ethnicity <- sqlQuery(sql,paste("SELECT ALF_PE, ETHN_EC_ONS_DATE_LATEST_CODE, ETHN_EC_ONS_DATE_LATEST_DESC FROM SAILW1429V.ETHN_1429 eth WHERE eth.ALF_PE IN (", paste(newly_matched_df$ALF_PE, collapse = ","), ")", sep=""))



matched_eth_swansea <- newly_matched_df %>%  merge(matched_ethnicity, by="ALF_PE",all.x = TRUE) 
matched_eth_swansea[21] <- lapply(matched_eth_swansea[21], addNA) # allows NA's to be read as character

matched_eth_swansea <- matched_eth_swansea %>%
  select(subclass, treatSeq, ALF_PE, treat, SEX, SEX_Desc, WOB, AGE_INDEXDATE, 
         AGEGROUP_STUDYSTART, AGE_STUDYSTART, LSOA2011_CD, WIMD, WIMD_DESC, RUC11_DESC, 
         IDENTIFIEDBY, FIRST_IDENTIFIED_DATE, FIRST_CARER_ASSMT, LATEST_CARER_ASSMT, 
         TOTAL_NUM_ASSESSMENTS, ETHN_EC_ONS_DATE_LATEST_CODE,ETHN_EC_ONS_DATE_LATEST_DESC)



```




# Export matched data to DB2
```{r echo = FALSE, include = FALSE}

sqlQuery(sql, "DROP TABLE SAILW1429V.PEJE_MATCHED_COHORT_SWANSEA_2;")

sqlQuery(sql, "CREATE TABLE SAILW1429V.PEJE_MATCHED_COHORT_SWANSEA_2
(
SUBCLASS VARCHAR(5)
, TREATSEQ INTEGER
, ALF_PE BIGINT
, TREATED INTEGER
, SEX INTEGER
, SEX_DESC VARCHAR(50)
, WOB DATE
, AGE_INDEXDATE INTEGER
, AGEGROUP_INDEXDATE VARCHAR(7)
, AGE_STUDYSTART INTEGER
, LSOA2011_CD VARCHAR(15)
, WIMD INTEGER
, WIMD_DESC VARCHAR(50)
, RUC11_DESC VARCHAR(50)
, FIRST_IDENTIFIED_BY VARCHAR(3)
, FIRST_IDENTIFIED_DATE DATE
, FIRST_ASSMT_DATE DATE
, LATEST_ASSMT_DATE DATE
, TOTAL_NUM_ASSESSMENTS INTEGER
, ETHNICITY_CD INTEGER
, ETHNICITY_DESC VARCHAR(7)
);")


# set fast = T for "missing columns in 'data'" error
sqlSave(sql, matched_eth_swansea, "SAILW1429V.PEJE_MATCHED_COHORT_SWANSEA_2", rownames = F, append = T , fast = F, verbose = T)

```
